Formalizing Hypothsis

### 2021-07-29 Documents/Report-Project/Formalize-hypotheses.Rmd
Update report with int e ext

$$
M_S < M_{Ax} = M_{Av} < M_F\\
P_S < P_{Ax} < P_{Av} = P_F\\
$$

```{r}
data_independent <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                        Score = c(0.05, 0.5, 0.5, 1, 0.05, 0.5, 1, 1))

@@

data_independent_grid$Problems <- rep(c(.05, .5, .5, 1), 4) + rep(c(.05, .5, 1, 1), each = 4)

@@

$$
M_SP_S< \{M_SP_{Ax;Av};\ M_{Ax;Av}P_S\} < \{ M_SP_F;\  M_FP_S\} < M_{Ax;Av}P_{Ax;Av} <  \{M_FP_{Ax;Av};\ M_{Ax;Av}P_F\} <  M_FP_F
$$

@@

data_interaction$Score <- c(.05, .15, .15, .40,
                            .10, .50, .50, .90,
                            .10, .50, .50, .90,
                            .40, .90, .90, 1.0)

>>>>

$$
M_S < M_{Ax} = M_{Av} < M_F\\
P_S < P_{Ax} < P_{Av} < P_F\\
$$

```{r}
data_independent <- data.frame(Parent = factor(rep(c("Mother", "Father"), each = 4), levels = c("Mother", "Father")),
                        Attachment = factor(rep(c("Secure", "Anxious", "Avoidant", "Fearful"), times = 2),
                                            levels = c("Secure", "Anxious", "Avoidant", "Fearful")),
                        Score = c(.05, .5, .5, 1, .05, .25, .75, 1))

@@

data_independent_grid$Problems <- rep(c(.05, .5, .5, 1), 4) + rep(c(.05, .30, .75, 1), each = 4)

@@

$$
M_SP_S< \{M_SP_{Ax;Av} = M_{Ax;Av}P_S\} < M_{Ax;Av}P_{Ax;Av} <  \{M_FP_{Ax;Av} = M_{Ax;Av}P_F\} <  M_FP_F
$$

With,
$$
M_{Ax}P_{Ax} = M_{Ax}P_{Av} = M_{Av}P_{Ax} = M_{Av}P_{Av}
$$

@@

data_interaction$Score <- c(.05, .15, .15, NA,
                            .10, .50, .50, .90,
                            .10, .50, .50, .90,
                            NA, .90, .90, 1.0)
